Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-07 paper/paper.tex
dayan2014 citation

In contrast, model-free methods require no prespecified knowledge of the environment (transition probabilities, identities of sensory input, etc.) or representation thereof, and the agent learns which state-action pairs lead to reward by sampling the world in a trial-and-error manner, and inferring long-run reward aggregates, using prediction error as an incentive. In so doing, such an intelligent agent ultimately
learns both a policy how to act on the environment and an implicit representations of the world 
\citep{sutton1998reinforcement}. Model-free RL may struggle with high numbers of states, but scales better with the time horizon than model-based RL \citep{strehl2006}. Drawing from a vast literature, we hope to show that the DMN can be expected to harbor the neurobiological hardware necessary to implement the principles of a model-free RL agent.

>>>>

In contrast, model-free methods require no knowledge of the environment (transition probabilities, identities of sensory input, etc.) or representation thereof, and the agent learns which state-action pairs lead to reward through sampling the world in trial-and-error manner, and predicting long-run reward aggregates, using prediction error as an incentive. In so doing, such methods ultimately learn both a policy and  implicit representations of the world / environment. This is what algorithms TD learning~\citep{sutton1998reinforcement}.
The distinction outlined above between model-free and model-based RL is similar to ~\citep{dayan2014}.

In terms of number of states, model-based RL scales better than model-free RL; in terms of the time horizon, model-free RL scales better~\citep{strehl2006}. Drawing from a vast literature, we will show that the DMN contains sufficient neurobiological hardware to implement model-free RL, at least in principle.
